|

### 2021-08-11 Real Dataset SV.Rmd
commit

Once more, most algorithms used (aside from SIS and Liu-West) seem to provide indistinguishable results. The SIS algorithm appears completely inadequate to describe the "true" volatility process: as we argued in section XX, the degeneracy of its weights on the particles prevents it from delivering a good enough approximation of the target distribution (\textit{check whether this is the correct intuition}). On top of that, it does not seem the case that the SIS algorithm, by falling short of the SV target distribution, ends up fitting the proxy better.\footnote{As we will now see, this seems instead to be the case for our preferred algorithms, namely those adopting adaptive resampling rules: a better approximation of the SV target filtering distribution yields slightly higher RMSEs and MAEs than those resulting from less accurate MC approximations.}\
On the other hand, the Liu and West filter offers the best performance among all filters, at least visually. This suggests that, since the Liu and West particle filter is built on a different underlying model than the other filters considered, this model may offer a better representation of the data analyzed. Once more, these considerations hold for all of the three indices.\

>>>>

Once more, most algorithms used (aside from SIS and Liu-West) seem to provide indistinguishable results. The SIS algorithm appears completely inadequate to describe the "true" volatility process: as we argued in section \ref{pf_intro}, the diverging variance of its weights on the particles prevents it from delivering a good enough approximation of the target distribution. On top of that, it does not seem the case that the SIS algorithm, by falling short of the SV target distribution, ends up fitting the proxy better.\footnote{As we will now see, this seems instead to be the case for our preferred algorithms, namely those adopting adaptive resampling rules: a better approximation of the SV target filtering distribution yields slightly higher RMSEs and MAEs than those resulting from less accurate MC approximations.}\
On the other hand, the Liu and West filter offers the best performance among all filters, at least visually. This suggests that, since the Liu and West particle filter is built on a different underlying model than the other filters considered, this model may offer a better representation of the data analyzed. Once more, these considerations hold for all of the three indices.\

### 2021-08-11 prova_knit_finale.Rmd
commit

```{r echo=FALSE, fig.align='center', fig.cap="Observations and filtered volatility, 3 indices", fig.height=4, fig.pos='H', fig.width=8, message=FALSE, warning=FALSE, results=F}

@@

ggarrange(plotobs7,plotobs8)
ggarrange(plotobs9,plotobs10)
ggarrange(plotobs11,plotobs12)

>>>>

```{r echo=FALSE, fig.align='center', fig.cap="Observations and filtered volatility, 3 indices", fig.height=7, fig.pos='H', fig.width=10, message=FALSE, warning=FALSE, results=F}

@@

ggarrange(plotobs7,plotobs8)
ggarrange(plotobs9,plotobs11)
plotobs10
plotobs12
